---
name: Matthew K de Gannes, PhD
position: Clinical Research Associate
address: 5400 Medpace Way, \tabularnewline Medpace, Inc., Cincinnati, OH 45227
phone: 413-588-4414
email: matthew.degannes@gmail.com
twitter: mdegannes
github: degama01
linkedin: mdegannes
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 000088
output: 
  pdf_document:
    latex_engine: pdflatex
    template: Working_Master_CV.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tinytex)
```

# Education and Qualifications

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "PhD, Environmental Genetics and Molecular Toxicology", "2014-2020", "University of Cincinnati College of Medicine", "Cincinnati, OH",
  "M.S., Environmental Health Sciences", "2012-2014", "University of Massachusetts Amherst", "Amherst, MA",
  "B.S., Biology", "2008-2012", "Gettysburg College", "Gettysburg, PA"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Employment History

```{r}
tribble(
  ~ Position, ~ Year, ~ Department, ~ Where,
  "Clinical Research Associate", "2020-present", "Clinical Monitoring Department", "Medpace, Inc., Cincinnati, OH",
  "Graduate Research Assistant", "2014-2020", "Department of Environmental and Public Health Sciences", "University of Cincinnati, Cincinnati, OH",
  "Research Intern", "2011", "Schroeder Institute for Tobacco Research and Policy Studies", "American Legacy Foundation, Washington, DC",
) %>% 
  detailed_entries(Position, Year, Department, Where)
```

# Leadership

```{r}
tribble(
  ~ Position, ~ Year, ~ Where,
  "President, Health Sciences Graduate Association", "2017-2018", "University of Cincinnati, Cincinnati, OH",
  "Vice-President, Health Sciences Graduate Association", "2016-2017", "University of Cincinnati, Cincinnati, OH",
  "Volunteer Chair, Health Sciences Graduate Association", "2016", "University of Cincinnati, Cincinnati, OH"
) %>% 
  detailed_entries(Position, Year, Where)
```



# Honors and Awards

```{r}
tribble(
  ~ Award, ~ Year, ~ Where,
  "Graduate Student Award for Exemplary Initiative", "2018", "University of Cincinnati, Cincinnati, OH",
  "Graduate Student Award for Exemplary Service in Life Sciences", "2018", "University of Cincinnati, Cincinnati, OH",
  "Graduate Student Association of the Year", "2018", "University of Cincinnati, Cincinnati, OH",
  "Graduate Student Government Research Fellowship", "2018", "University of Cincinnati, Cincinnati, OH",
  "Third Place in Poster Presentations, Research Day", "2013", "University of Massachusetts Amherst, Amherst, MA",
  "Fall Semester Commendation List", "2012", "Gettysburg College, Gettysburg, PA",
  "Spring Semester Dean's List", "2011", "Gettysburg College, Gettysburg, PA",
  "Fall Semester Commendation List", "2011", "Gettysburg College, Gettysburg, PA",
  "Spring Semester Dean's List", "2009", "Gettysburg College, Gettysburg, PA",
  "Fall Semester Dean's List", "2009", "Gettysburg College, Gettysburg, PA"
) %>%
  detailed_entries(Award, Year, Where)
```
  
# Service
```{r}
tribble(
  ~ Position, ~ Year, ~ Where,
  "SciShortform Science Writing Editor", "2020", "Online SciShortform Group",
  "Biomedical Careers and Research Presenter", "2019", "Cincinnati Museum Center Children's Summer Camp",
  "Dean's Council Graduate Student Representative", "2017-2018","University of Cincinnati College of Medicine",
  "Three Minute Thesis Judge", "2017", "University of Cincinnati College of Medicine",
  "Co-developer of Project Citizen Science Initiative", "2016-2017", "University of Cincinnati",
  "Judge for Children's Science Posters", "2016", "Southwest Ohio Science and Engineering Expo",
  "Faculty Search Committee for Environmental Health Sciences Division", "2012-2013", "University of Massachusetts Amherst"
) %>% 
  detailed_entries(Position, Year, Where)
```

# Teaching Experience
```{r}
tribble(
  ~ Position, ~ Year, ~ Course, ~ Where,
  "Tutor", "2016", "Molecular and Cellular Biology", "University of Cincinnati",
  "Teaching Assistant", "2014", "Introduction to Environmental Health Sciences", "University of Massachusetts Amherst",
  "Teaching Assistant", "2012", "Introduction to Environmental Health Sciences", "University of Massachusetts Amherst"
) %>% 
  detailed_entries(Position, Year, Course, Where)
```

# Conference Presentations
  1. **de Gannes, M.**, Ko, C.I., Biesiada, J., Zhang, X., Medvedovic, M., Puga, A. (2019). TCDD Alters Dynamic DNA Methylation Patterns Crucial for Cardiomyocyte Maturation and Implicated in Disease. Ohio Valley Society of Toxicology Annual Meeting. *Cincinnati, OH, 2019*
  2. Kreslake, J.M., Cantrell, J., Vallone, D.M., Tacelosky, M., Ganz, O. Dubois, P., **de Gannes, M.**, Pearson, J.L., Kirchner, T.R. (2012). Development and Implementation of a Mobile Phone-based System for Surveillance of Point-of-Sale Tobacco Marketing Tactics. Society for Research on Nicotine and Tobacco Annual Meeting. *Houston, TX, 2012*
  
# Conference Abstracts
  1. **de Gannes, M.K.**, Ko, C.I., Biesiada, J., Zhang, X., Medvedovic, M., Puga, A. (2020). TCDD Alters Dynamic DNA Methylation Patterns Crucial for Cardiomyocyte Maturation and Implicated in Disease. Society of Toxicology Annual Meeting. *Anaheim, CA, 2020*

# Research Dissertations

## PhD Dissertation
  1. **de Gannes, M.** Dioxin Impact on Cardiac Development, Structure, Function, and Health, and Implications for Disease. PhD Dissertation.  University of Cincinnati College of Medicine.  
    + **Advisor:** Dr. Alvaro Puga (Department of Environmental and Public Health Sciences)
    
## M.S. Thesis
  1. **de Gannes, M.** Rapid Method of Processing Sperm for Nucleic Acid Extraction in Clinical Research. M.S. thesis. University of Massachusetts Amherst.  
    + **Advisor** Dr. Richard Pilsner (Department of Environmental Health Sciences)
    
# Publications
  
## Journal Articles
  1. **de Gannes, M.**, Koch, S., Puga, A., & Rubinstein, J. (2021). Developmental and Lifelong Dioxin Exposure Induces Measurable Changes in Cardiac Structure and Function in Adulthood. *Scientific Reports*, **11**(1), 10378. doi:10.1038/s41598-021-89825-w  
  2. **de Gannes, M.**, Ko, C.I., Zhang, X., Biesiada, J., Niu, L., Koch, S., Medvedovic, M., Rubinstein, J., & Puga, A. (2020). Dioxin Disrupts Dynamic DNA Methylation Patterns in Genes that Govern Cardiomyocyte Maturation. *Toxicological Sciences*, **178**(2), 325-337. doi:10.1093/toxsci/kfaa153
  3. Ko, C. I., Fan, Y., **de Gannes, M.**, Wang, Q., Xia, Y., & Puga, A. (2016). Repression of the Aryl Hydrocarbon Receptor Is Required to Maintain Mitotic Progression and Prevent Loss of Pluripotency of Embryonic Stem Cells. *Stem Cells*, **34**(12), 2825-2839. doi:10.1002/stem.2456
  4. Wu, H., **de Gannes, M. K.**, Luchetti, G., & Pilsner, J. R. (2015). Rapid Method for the Isolation of Mammalian Sperm DNA. *Biotechniques*, **58**(6), 293-300. doi:10.2144/000114280  
    + Co-first author